Full 18s Community composition

### 2019-11-02 code/whole_18s_community_compare.Rmd
new paths for input files

```{r input, include=F}
tree_path <- here("intermediate_output/tree/full_18s/all_18s_aligns.fasta.treefile")
all_18s_tree <- read.tree(tree_path)

ra_path <- here("data/clean/clean_18s_ra.csv")
ra <- read_csv(ra_path)

assignment_path <- here("data/clean/clean_silva_18s_assignments.csv")
assign <- read_csv(assignment_path)

field_path <- here("data/clean/field_clean.csv")
field <- read_csv(field_path)

alias_path <- here("data/sample_aliases.csv")
alias <- read_csv(alias_path)
```

@@

```{r nmds_stress, include=F}
mono <- metaMDS(weighted_unifrac_distm)
mono
```

@@

# order algae, fungi, protists, other
phylum_ord <- c("Chlorophyta_ph", "Ochrophyta","Basidiomycota", "Ascomycota", "Chytridiomycota", "Ciliophora","Cercozoa","Protalveolata", "Phragmoplastophyta")

ggplot(p, aes(x=sample_id %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=phylum), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~phylum %>% fct_relevel(phylum_ord), switch = "x") +
  labs(title = "Relative abundance plot of 18S phyla", x="Sample ID (from lowest to highest elevation)") +
  cust_theme
```

@@

>>>>

```{r input, include=F}
all_18s_tree <- read.tree(here("output/tree/full_18s/all_18s_aligns.fasta.treefile"))
ra <- read_csv(here("data/03_filtered/18s/filtered_cleaned_18s_rel_abund.csv"))
assign <- read_csv(here("data/02_tidied/tidied_silva_18s_assignments.csv"))
field <- read_csv(here("data/02_tidied/tidied_field.csv"))
```

@@

```{r nmds_stress, include=F}
set.seed(123)
mono <- metaMDS(weighted_unifrac_distm)
mono
```

@@

# order algae, fungi, protists, other
phylum_ord <- c("Chlorophyta", "Ochrophyta","Basidiomycota", "Ascomycota", "Chytridiomycota", "Ciliophora","Cercozoa","Protalveolata", "Phragmoplastophyta")

rel_abund_phyla <- ggplot(p, aes(x=sample_id %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=phylum), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~phylum %>% fct_relevel(phylum_ord), switch = "x") +
  labs(title = "Relative abundance plot of 18S phyla (SILVA assignments)", x="Sample ID (from lowest to highest elevation)") +
  cust_theme
rel_abund_phyla
```

@@

```{r output, include=F}
dir.create(here("manuscript/figs/S5_18s"))
ggsave(filename = here("manuscript/figs/S5_18s/18s_rel_abund.pdf"), plot=rel_abund_phyla)
```
